---
title: "CSE350 Week 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Task 4: Visualizing Large Distributions
https://byui.instructure.com/courses/134980/pages/task-4-visualizing-large-distributions?module_item_id=17322326

## Load Data
```{r}
install.packages("nycflights13")
install.packages("ggplot2")
```


```{r}
library(ggplot2)
library(nycflights13)
```

## Preview the data
```{r}
head(nycflights13::flights)
?flights
```
```{r, include=FALSE}
# pairs(flights)
```

## [ ] Find an insightful relationship between two of the variables (aka, columns).

```{r distance x air_time}
ggplot(flights) + 
  geom_point(aes(x=distance, y=air_time))
```

## [ ] For each of the two variables you chose, create a chart that summarizes the distribution of the variable. (2 charts total)

```{r}
par(mfrow=c(1,3))

ggplot(flights) + 
  geom_histogram(aes(x=distance))

ggplot(flights) + 
  geom_histogram(aes(x=air_time))

```

## [ ] Visualize the bivariate relationship (At least 1 chart). If you don't know what "bivariate" means, try google!

See "distance x air_time" chunk.

## [ ] Write a short paragraph or two answering the following questions:
### What do you learn about the data from looking at the charts?
They both have a similar shape in their distribution which I think makes sense since they are a very linear relationship with each other in the bivariate plot.

### Why did you choose to make those types of charts?
A histogram is great at showing the distribution of a variable, and a scatterplot is good at plotting two numeric variables in relation to each other. I simply choose them because they were simple ways to visualize these data types.


## [ ] Create an R Markdown report that has the graphs and discussion mentioned above. Knit it to an .html file and make sure you keep the .md file.

## [ ] Do not submit your files anywhere. On Friday we will learn how to submit them on GitHub.
